Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-17 Latex/tex/pr.tex
fig2

\section{Introduction}
Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the challenges in a best way.  
The Idea of O-RAN comes from two opinion. Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more open and smarter than previous generations. Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}. \newline
The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities. Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
To communicate between BBU-Pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity. Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.\newline
xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features. Control plane is decoupled from User plane. In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces is introduced\cite{xran}.
\begin{figure}[H]
  \centering
    \includegraphics[scale=0.55]{c2}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure} 
To evolve servicing in 5G, separation of elements of software and hardware of network is deployed in network functions virtualization (NFV) technology. In this technology, the functionality of networks is virtualized and divided to blocks of virtual network function (VNF).
Responsibility of wireless systems of the fifth generation covers a wide range types of services. In order to provide the requirement of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks. Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing. In Core-RAN Slicing, each slice of RAN is mapped to slices of Core. Also, UEs classified to group of services according to their requirements. In addition, each service is connected to one or more Core-RAN slices base on the resource of slices.
Using cloud-computing in BBU-Pool, enhance performance of system by virtualizing resources
into virtual machines (VMs).
Each VM has a computing processor mapped to Virtual Network Functions (VNFs) which processed arrival data. Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}. 
\newline  
In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum rate. Moreover, in \cite{frdl,luong2018novel,luong2018novel1} minimization of cost obtained by power consumption and cloud processing is applied. Limited fronthaul capacity is considered. Also processing delay of each VM and wireless transmission delay is bounded.\newline  
In this paper, as  depicted in figure \ref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
their service requirements. Also RAN is decoupled to slices to provide services needs. Optimal power allocation and joint connecting slices to services is applied. In addition, mapping slices to physical resources is taken to account.

@@

Suppose that there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ Physical Resource Blocks (PRBs) as it is defined in standard of LTE that the bandwidth (BW) of channel is divided to PRBs in time series \cite{lee2018dynamic}. All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}. Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
Suppose that we have two processing layer in BBU-Pool of O-RAN system. The lower layer is consist of PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.

@@

for simplicity, suppose ach VM is connected to a VNF.
Each VNF in both layers maps to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in first layer and $M_{s_2}$ VNFs in second layer. All VNFs in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively. 

@@

\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}};

@@

\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v};

@@

Where $\boldsymbol{x}_{ \mathcal{R}_s} = [x_{ r_{(s,1)}},...,x_{ r_{(s,\mathcal{R}_s)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector for the $s$-th set of Network slice,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.
\\

@@

$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks (PRB) to UE.
Also as defined before, $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$ 

@@

$\mathcal{U}_v$. 
The channel vector from the RRH of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below

@@

\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
represents the large scale fading matrix. Here, it is assumed we have perfect channel state information(CSI).
\\
Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as follow
\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}

@@

 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{vs}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{ys} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{vs}}_{\text{(quantization noise interference)}}.

@@

where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$

@@

It is assumed that interference signal for each UE, is applied from UEs which are using same PRB.
If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$. Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in equation \eqref{eq1} and \eqref{eq2}.\newline

@@

from equation \eqref{eq3} we have

@@

\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{vs} + \sigma_{q_{r(s,j)}}^2.

@@

As a result the user data capacity on the fronthual link between BBU and the $j^{th}$ RRH in $s^{th}$ slice is formulated as below

@@

C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{vs}}{ \sigma_{q_{r(s,j)}}^2})},

@@

Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE in $v^{th}$ service. 
Therefore, the mean arrival data rate of UEs in $s^{th}$ slice in the first layer is 
$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  

@@

It is assumed that there are dispatchers in each layer for each slice to divide the incoming traffic to VMs.
Suppose the baseband processing of each VM is depicted as a M/M/1 processing queue.
Each packet is routed by one of VMs of slices. So the mean delay of slice $s$ which is related to incoming traffic rate routed to
each VM in first layer can be written as follow

@@

d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}}

@@

Also, the delay in $s^{th}$ slice in second layer can be formulated as below

@@

d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}

@@

In addition, the arrival data rate to the queue of wireless transmission
 is equal to the arrival data rate of dispatcher.

@@

d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}}

@@

Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}R_{u(v,i)}$.
We define a new parameter which indicates mean delay of each slice

@@

D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s

@@

\subsection{Physical Resource}
Assume each VM is mapped to one virtual network function (VNF) for simplicity. Each VNF requires

@@

\bar{\Omega}_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \}

@@

Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU.
Moreover total amount of required RAM, Memory and CPU of all VNFs in a slice is a three dimension vector which is defined as

@@

\bar{\Omega}_{s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{(f,s)}

@@

Where, $F_s = M_{s_1} + M_{s_2}$ is the total number of VNFs in slice $s$.
\newline
Also, in the Core Network (CN), there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's needs.
The amount of RAM, Memory and CPU is denoted respectively by $\tau_{R_{j}}, \tau_{M_{j}}$ and $\tau_{C_{j}} $ for $j^{th}$ DC.

@@

\tau_j = \{\tau_{R_{j}}, \tau_{M_{j}}, \tau_{C_{j}} \}

@@

\hat{\tau}_j &= w_R \tau_{R_{j}} + w_M \tau_{M_{j}} + w_C \tau_{C_{j}}

@@

Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ are the weight of RAM, Memory and CPU.

@@

One of the most important parameters to estimate the optimality of the system is energy efficiency which is represented as sum-rate to sum-power as follow

@@

Assume the power consumption of baseband processing at each data center that is mapped to VNFs of a slice is depicted as

@@

\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi

@@

Where, $y_{s,d}$ is a binary variable which indicates whether $d^{th}$ data-center is mapped to VNFs of $s^{th}$ slice or not.\\

@@

& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \label{c21} \\
& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s,\label{c23} \\

@@

Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]  \forall s , \forall d $. 
Equation \eqref{c11}, \eqref{c12} indicates respectively that the power of each RRH do not exceed the maximum power and power of each UE is a positive integer value. Also \eqref{c13} shows that the rate of each UE is more than a threshold. \eqref{c14} and \eqref{c15} depicts respectively that the capacity of fronthaul link is limited and the delay of receiving signal should be less than a threshold.  

@@

ensure that each service is mapped to one or more slice.
Also, \eqref{c23} guarantee that each slice (VNFs in two layers of slice) has been placed to one or more physical resources (DC). Moreover, in \eqref{c22}  $\mathfrak{z}\in \{M,R,C\}$, which supports 

@@

The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem A and B. The problem A is introduced as bellow

@@

& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s

@@

\text{subject to} \quad & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\

@@

We want to solve \eqref{constraints1}. Since the problem is non-convex and NP-Hard iterative algorithm is applied.
To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} to 

@@

\State Set $a_{ij} = 1$

@@

\State Set $a_{ij} = 0$;

@@

See Appendix A

@@

In order to make equation \eqref{constraints1} as a standard form of convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.

@@

&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{vs}.\\ 

@@

$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}$. Also 

@@

@@

In this subsection, we want to solve equation \eqref{constraints2} which is the placement of virtual resources to physical resource in order to minimize the number of using DCs. 

>>>>

\section{Introduction}
Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the challenges in a best way.  
The Idea of O-RAN comes from two opinion. Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more open and smarter than previous generations. Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}. \newline
The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities. Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
To communicate between BBU-Pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity. Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.\newline
xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features. Control plane is decoupled from User plane. In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces is introduced\cite{xran}.
\begin{figure}[H]
  \centering
    \includegraphics[scale=0.55]{c3}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure} 
To evolve servicing in 5G, separation of elements of software and hardware of network is deployed in network functions virtualization (NFV) technology. In this technology, the functionality of networks is virtualized and divided to blocks of virtual network function (VNF).
Responsibility of wireless systems of the fifth generation covers a wide range types of services. In order to provide the requirement of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks. Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing. In Core-RAN Slicing, each slice of RAN is mapped to slices of Core. Also, UEs classified to group of services according to their requirements. In addition, each service is connected to one or more Core-RAN slices base on the resource of slices.
Using cloud-computing in BBU-Pool, enhance performance of system by virtualizing resources
into virtual machines (VMs).
Each VM has a computing processor mapped to Virtual Network Functions (VNFs) which processed arrival data. Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}. 
\newline  
In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum rate. Moreover, in \cite{frdl,luong2018novel,luong2018novel1} minimization of cost obtained by power consumption and cloud processing is applied. Limited fronthaul capacity is considered. Also processing delay of each VM and wireless transmission delay is bounded.\newline  
In this paper, as  depicted in figure \ref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
their service requirements. Also RAN is decoupled to slices to provide services needs. Optimal power allocation and joint connecting slices to services is applied. In addition, mapping slices to physical resources is taken to account.

@@

Suppose that there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs) as it is defined in standard of LTE that the bandwidth (BW) of channel is divided to PRBs in time series \cite{lee2018dynamic}. All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}. Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
Suppose we have two processing layer in BBU-Pool of O-RAN system. The lower layer is consist of high-PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.

@@

For simplicity, suppose each VM is connected to a VNF.
Each VNF in both layers connects to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in first layer and $M_{s_2}$ VNFs in second layer. All VNFs in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively. 

@@

\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}};

@@

\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v};

@@

Where $\boldsymbol{x}_{ \mathcal{U}_v} = [x_{ u_{(v,1)}},...,x_{ u_{(v,\mathcal{U}_v)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector of UEs in $v^{th}$ set of service,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.\newline

@@

$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter, demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
$\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$ 

@@

$\mathcal{U}_v$, besides. 
%The channel vector from the RRH of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
%\begin{equation}
%\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
%\end{equation}
%where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
%represents the large scale fading matrix.
What's more, it is assumed we have perfect channel state information(CSI).\newline
Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below

@@

\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.

@@

 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}}.

@@

Where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$

@@

As it is clear, Interference signal for each UE is comming from UEs using the same PRB.
If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$. Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in  \eqref{eq1} and \eqref{eq2}.\newline

@@

from \eqref{eq3} we have,

@@

\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.

@@

As a result the rate of users on the fronthual link between BBU-Pool and the $j^{th}$ RRH in $s^{th}$ slice is formulated as 

@@

C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s}}{ \sigma_{q_{r(s,j)}}^2})},

@@

Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE of $v^{th}$ service. 
Therefore, the mean arrival data rate of UEs connect to $s^{th}$ slice in the first layer is 
$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}\lambda_{u(v,i)}$.  

@@

It is assumed there are dispatchers in each layer for each slice to divide the incoming traffic to VNFs \cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as a M/M/1 processing queue.
Each packet is routed by one of VNFs of slices. So the mean delay of slice $s$ which is related to incoming traffic rate routed to
each VNF in first layer can be written as follow

@@

d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}}.

@@

Also, the delay of $s^{th}$ slice in second layer is

@@

d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}.

@@

In addition, $d_{s_{tr}}$ is another delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission
 is equal to the arrival data rate of dispatchers for each slice that divide data rates and transmit divided rates to VNFs.

@@

d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}};

@@

Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{v,s}R_{u(v,i)}$.
Mean delay of each slice is

@@

D_{s} = d_{s_1} + d_{s_2} + d_{s_{tr}} \forall s.

@@

\subsection{Physical Data Center Resource}
Each VNF requires

@@

\bar{\Omega}_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \};

@@

Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU, respectively.
Moreover total amount of required RAM, Memory and CPU of all VNFs of a slice is a three dimension vector which is defined as

@@

\bar{\Omega}_{s}^{tot} = \sum_{f=1}^{M_{s_1} + M_{s_2}}\bar{\Omega}_{(f,s)};

@@

Also, there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's requirements.
The amount of RAM, Memory and CPU is denoted by $\tau_{R_{j}}, \tau_{M_{j}}$and $\tau_{C_{j}} $ for $j^{th}$ DC, respectively .

@@

\tau_j = \{\tau_{R_{j}}, \tau_{M_{j}}, \tau_{C_{j}} \};

@@

\hat{\tau}_j &= w_R \tau_{R_{j}} + w_M \tau_{M_{j}} + w_C \tau_{C_{j}},

@@

Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ are the weight of RAM, Memory and CPU that is used for Algorithm \ref{alg3}.
In this system model the placement of physical data center resources to VNFs is considered. $y_{s,d}$ is a binary variable indicates whether $d^{th}$ data-center is connected to VNFs of $s^{th}$ slice or not.

@@

One of the most important parameters to estimate the optimality of the system is energy efficiency which is represented as a sum-rate to sum-power 

@@

Assume the power consumption of baseband processing at each data center that is connected to VNFs of a slice is depicted as

@@

\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi.

@@

@@

& \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s, \label{c21} \\
& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} &&\quad \forall s,\label{c23} \\

@@

Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{v,s}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]   \forall s ,  \forall d $. 
\eqref{c11} and \eqref{c12} indicate that the power of each RRH do not exceed the maximum power and power of each UE is a positive integer value, respectively. Also \eqref{c13} shows that the rate of each UE is more than a threshold. \eqref{c14} and \eqref{c15} depicts that the capacity of fronthaul link is limited and the delay of receiving signal should be less than a threshold, respectively.  

@@

ensures that each service is connected to one or more slices.
Also, \eqref{c23} guarantees that each slice (VNFs in two layers of slices) has been placed to one or more physical resources of DCs. Moreover, \eqref{c22}  $\mathfrak{z}\in \{M,R,C\}$, supports 

@@

The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem A and B since the variables can be obtained independently. The problem A is defined as 

@@

& \sum_{s=1}^{S}a_{v,s} \geq 1 &&\quad \forall s

@@

\text{subject to} \quad & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{v,s} \geq 1\times\sum_{v=1}^{V}a_{v,s} &&\quad \forall s, \\

@@

We want to solve \eqref{constraints1}. Since the problem is non-convex and NP-Hard, iterative algorithm is applied.
To solve the problem and obtain optimum $\boldsymbol{A}$ and $\boldsymbol{P}$ we divide problem \eqref{constraints1} into 

@@

\State Set $a_{i,j} = 1$

@@

\State Set $a_{i,j} = 0$;

@@

See \cite{aaa}, Appendix A

@@

In order to make \eqref{constraints1} as a standard form of convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.

@@

&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.\\ 

@@

$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also 

@@

Firstly, by fixing power of each UE, $\boldsymbol{A}$ is obtained using Algorithm \eqref{alg}. Then by using sub-gradient method, \eqref{secondsub} is solved and iteratively solve these problems until variables converge.

@@

In this subsection, we want to solve  \eqref{constraints2} which is the placement of virtual resources to physical resource in order to minimize the number of using DCs. 
